1. Import untidy Lord of the Rings data
```{r}
# essential to load tidyverse package!
library(tidyverse)
# read in data files: can do this
fship <- read_csv("data/The_Fellowship_Of_The_Ring.csv")
# or this: fship <- read_csv(file.path("data", "The_Fellowship_Of_The_Ring.csv"))
# DO NOT use read.csv, as it does not create a tibble (a type of data frame)
ttow <- read_csv("data/The_Two_Towers.csv")
rKing <- read_csv("data/The_Return_Of_The_King.csv")
```

2. Collect untidy Lord of Rings data into a single data frame
We want to glue the data together into a single data frame, stacking them up row wise (row binding).
```{r}
lotr_untidy <- bind_rows(fship, ttow, rKing) # use bind_rows()
lotr_untidy # a tibble
```
Assembling one large data object from many little ones is a common data preparation task.
A good guiding principle is to glue the pieces together as early as possible.

3. Tidy the untidy Lord of Rings data
We need to create a new variable, Gender, to track whether each count refers to males or females.
Then we can gather the word counts into a single variable.
```{r}
# use gather() from the tidyr package
lotr_untidy <- gather(lotr_untidy, key = 'Gender', value = 'Words', Female, Male)
```





